---
---
title:"An Analysis of Energy-Related CO2 Emissions in North Carolina and US."
author: "Yin-Chia Yang, Gary Alvarez, Sayra Martinez, Miaojun Pang"
date: "Spring 2024"
output:
  html_document:
    df_print: paged
geometry: margin=2.54cm
fig_height: 3
fig_width: 4
editor_options:
  chunk_output_type: console
---
------------------------------------------------------------------------


```{=tex}
\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage
```

## github repository
https://github.com/yangeline/YangMartinezAlvarezPang.git

```{r setup, include=FALSE}
# Set your working directory
getwd()

# Load your packages
library(ggplot2)
library(forecast)
library(tidyverse)
library(dplyr)
library(tidyr)
library(trend)
library(zoo)
library(lubridate)
library(here)
library(cowplot)

# Set your ggplot theme
project_theme <- theme_light(base_size = 12) +
                theme(axis.text = element_text (color = "green"), legend.position = "bottom")

# Load your datasets
here()
NC_Emission <- read.csv("./Data/Raw Data/NC_Emissions.csv", stringsAsFactors = TRUE)



```

# Rationale and Research Questions

Rationale The urgency of climate change, propelled by rising levels of
CO2 emissions, necessitates a detailed understanding of emission
sources, patterns, and impact. Energy consumption, particularly the
burning of fossil fuels for electricity, heat, and transportation, is a
significant contributor to global CO2 emissions. 

Understanding these emissions on a granular level, such as by state and sector, 
is critical for developing effective mitigation strategies. North Carolina, like
many states, faces its unique challenges and opportunities in managing
CO2 emissions due to its specific industrial activities, energy mix, and
policy environment. 

Given the vast amount of data available, there's a
pressing need for analytical tools that can simplify this complexity
into actionable insights. By leveraging R, a powerful tool for data
analysis, this project aims to provide a comprehensive analysis of North
Carolina's CO2 emissions within the wider context of the United States,
identifying key areas for policy intervention and technological
innovation.

Research Questions

1.  What are the primary sources of CO2 emissions in North Carolina, and
    how do these compare with national trends?
```{r}

```

2.  Which policies and technologies have contributed to increases or
    decreases in CO2 emissions within North Carolina, and how can these
    be applied or modified for better results?

or 2. How do CO2 emissions in North Carolina vary by sector
(residential, commercial, industrial, and transportation), and what
trends can be identified over time?

\newpage

# Dataset Information

\newpage

# Exploratory Analysis

\newpage

# Analysis

## Question 1: \<insert specific question here and add additional subsections for additional questions below, if needed\>

## Question 2:

\newpage

# Summary and Conclusions

\newpage

# References

\<add references here if relevant, otherwise delete this section\>
